### 2015-12-16 outline.tex
add section on cross-industry variation

>>>>

\vskip.5in
Possible cross-industry variation
\begin{itemize}
	\item Industry / lobby gets richer / more insulated for five years
		\begin{itemize}
			\item This could lead to differences in budget constraint if that were in model
			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
				\begin{itemize}
					\item \textbf{Q}: This is one of the arguments for escape clause, no?
				\end{itemize}
		\end{itemize}
	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
\end{itemize}
